### 2013-02-13 exam5/1.tex
First draft of JSON problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{19}

>>>>

\begin{problem} \pts{??}

JSON is a lightweight data-interchange format.  It is widely used on
the web and plays exactly the role of S-Expressions in universe
programs, but for JavaScript programs.  It's used by folks like Google
and there's tons of data on the web that's available in the JSON
format.  So as to not be left out of the fun, your co-op employer has
asked you to design an object representation of JSON to incorporate
into their 2 million lines of {\tt class/2} code.  To start things off
simply, here are some examples of what we'll call ``JSON, Jr.'':

\begin{verbatim}
"this is JSON"
{ "this is JSON", "Jr." }
{ {}, { "So", "is" }, "this" }
\end{verbatim}
The first example is just a string.  The second is an ``array'' of two
JSON elements, which are both strings.  The third is another array,
but of three elements: the first is an array of zero elements, the
second is an array of two strings, and the third is a string.

\begin{enumerate}
\item Design an object-based data representation for JSON, Jr.
\newpage
\item Design a method for counting the number of strings in a JSON,
  Jr.~object.
\newpage
\item Among the 2M lines of code your employer maintains are 30,000
  lines of code devoted to implementations of the {\tt
    StringPred} interface, which is:
\begin{verbatim}
;; A StringPred implements
;; - apply : String -> Boolean
\end{verbatim}
These objects represent predicates on strings.  Now that your JSON,
Jr. library is in place, they've decided to put their predicates to
use in searching a large corpus of JSON data.  To accomodate this,
design the following method for JSON, Jr.~objects:
\begin{verbatim}
;; Find the first string in this JSON Jr object satisfying
;; given predicate, or #f if there's no such string.
;; find : StringPred -> String or #f
\end{verbatim}
\end{enumerate}

\end{problem}

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]
\newpage
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{19}
